---
title: "Using mocapGrip"
author: "Jonathan Keane"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package contains all of the code used to process and analyze motion capture data from experiments that use a reach to grasp, size estimation, and gesture about objects (and actions taken on them) that are (sometimes) in a visual illusion paradigm.

## Data processing pipline

See the project's readme file for information about this.

## Report writing

In order to make reports about the data, first you need to load the data in with the command `readExtractedMocapData()` after that, you can use the `makeReport()` function to write the report for all of the types of analyses (*action*, *estimation*, etc.) that were extracted with `readExtractedMocapData()`. the `makeReport()` function returns the data obejct with models included if it is needed for other uses.  A full example is below: 

```{r, fig.show='hold', eval=FALSE}
dataNew <- readExtractedMocapData("~/Dropbox/mocap/gripStudy/extractedGestData/", c("action", "estimation",  "release", "estMaxGrip"), includeFullData = FALSE)

dataModeled <- makeReport(dataNew, reportPath="./reportActionExtimationFromGestureTrials.Rmd")
```

```{r, eval=FALSE, echo=FALSE}
# run the report on new gesture data.
dataNewGest <- readExtractedMocapData("~/Dropbox/mocap/gripStudy/extractedGestData/", c("action", "estimation", "gestMaxGrip", "gestMove"), includeFullData = FALSE)

dataNewGestModeled <- makeReport(dataNewGest, reportPath="./reportGesture.Rmd")


# replication
pureReplicationModeled <- makeReport(pureReplication, reportPath="./reportReplication.Rmd")


```
